Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-08-20 write-up/covid-writeup.tex
Fixing the figures in paper

\begin{figure}[!th]
\centering
\includegraphics[width = 0.4\textwidth]{../figs/mem_heatmap_article.png}
\caption{Imperfect testing adjustment: relative frequency $f_1/f_0$ (x-axis) against odds ratio (y-axis) for $FP=0.024$ and $FN=0.13$. Color scaled so blue = $-10$, white = $0$, and red = $10$.}
%\textcolor{red}{NEED TO DO FOR FP = 0.05 and FN = 0.3}}
\label{fig:heatmap}
\vspace{-0.3cm}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/sir_ratio.png}
 \caption{Ratio estimator}
 \label{fig:ratio-bias}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/sir_rt.png}
 \caption{Effective reproductive rate estimator}
 \label{fig:r0-bias}
\end{subfigure}
\caption{Potential bias due to self-selection and measurement error from a deterministic SIR model with $\beta = 1.2$ (black) and $\gamma = 0.15$.  Here we assume $f = 0.02$, $FP = 0.024$, $FN = 0.30$, and use a range of relative sampling fraction $M = f_1/f_0$.}
\label{fig:rates}
\end{figure}

>>>>

\begin{figure}[!th]
\centering
\includegraphics[width = 0.7\textwidth]{../figs/mem_heatmap.png}
\caption{Imperfect testing adjustment: relative frequency $f_1/f_0$ (x-axis) against odds ratio (y-axis) for $FP=0.024$ and $FN=0.13$. Color scaled so blue = $-10$, white = $0$, and red = $10$.}
%\textcolor{red}{NEED TO DO FOR FP = 0.05 and FN = 0.3}}
\label{fig:heatmap}
\vspace{-0.3cm}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/sir_ratio.png}
 \caption{Ratio estimator}
 \label{fig:ratio-bias}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
 \centering
 \includegraphics[width=.9\linewidth]{../figs/sir_rt.png}
 \caption{Effective reproductive rate estimator}
 \label{fig:r0-bias}
\end{subfigure}
\caption{Potential bias due to self-selection and measurement error from a deterministic SIR model with $\beta = 1.2$ (black) and $\gamma = 0.15$.  Here we assume $f = 0.02$, $FP = 0.024$, $FN = 0.30$, and use a range of relative sampling fraction $M = f_1/f_0$. \textcolor{red}{FIX!}}
\label{fig:rates}
\end{figure}
